Precise predictions for same-sign W-bosons scattering at the LHC

### 2018-01-12 Draft/article.tex
LO scan : text added
Add Simon as author
Addition of some paragraphs
minimal changes
Add a motivation and extend the introduction
- added a motivation (first paragraph)
- extended or added some explanations
- changed the process to include the `+ X`, since we are inclusive;
  TODO: make sure this is also used in the remaining document
- changes `section` and `Section` to `Sec.` if they are not at the
  beginning of a sentence (in `macros.tex` there are abbreviations for
  it so I assume that is the "correct" style)
- corrected some spelling mistakes

%% Main-Version Draft
\documentclass[twocolumn,epjc3]{svjour3} % use the EPJC template, two columns
%%\documentclass[epjc3]{svjour3} % use the EPJC template, one column
\smartqed  % flush right qed marks, e.g. at end of proof
%% -------------------------------
%% |          Packages           |
%% -------------------------------
 \usepackage{amsmath}
 \usepackage{graphicx}
 \usepackage[merge,numbers,compress]{natbib}
 \usepackage[T1]{fontenc}
 \usepackage{booktabs}
 \usepackage{xcolor} 
 \usepackage{xspace}
 \usepackage{dcolumn}
 \usepackage{hyperref}
 \usepackage{caption}
 \usepackage{tabularx}
 \usepackage{lmodern}
% \usepackage
% [subrefformat=parens,position=top,skip=-15pt,margin=15pt,justification=justified,singlelinecheck=false]
% {subcaption}

@@

\author{Benedikt Biedermann\thanksref{wurz}
\and
Simon Brass\thanksref{sieg}
\and
Ansgar Denner\thanksref{wurz}
\and
Stefan Dittmaier\thanksref{frei}
\and
Michele Grossi\thanksref{pavia,ibm}
\and
Alexander Karlberg\thanksref{uzh} 
\and
Mathieu Pellen\thanksref{wurz,e1}
\and
Giovanni  Pelliccioli\thanksref{unito}
\and
Michael Rauch\thanksref{kit}
\and
J\"urgen Reuter\thanksref{desy}
\and
Vincent Rothe\thanksref{desy} 
\and
Christopher Schwan\thanksref{frei}
\and
Pascal Stienemeier\thanksref{desy}
\and
Marco Zaro\thanksref{nikh,e2}
}

\thankstext{e1}{e-mail: mpellen@physik.uni-wuerzburg.de}
\thankstext{e2}{e-mail: m.zaro@nikhef.nl}

\institute{Universit\"at W\"urzburg, %
Institut f\"ur Theoretische Physik und Astrophysik,  %
Emil-Hilb-Weg 22, %
97074 W\"urzburg, %
Germany\label{wurz} 
\and
Universit\"at Siegen, Department Physik, %
 Walter-Flex-Str.3, %
57068 Siegen, Germany\label{sieg}
\and
Albert-Ludwigs-Universit\"at Freiburg, Physikalisches Institut, %
 Hermann-Herder-Str.\ 3, %
79104 Freiburg, Germany\label{frei}
\and
Universit\'a di Pavia, Dipartimento di Fisica and INFN, Sezione di Pavia, %
Via A. Bassi 6, %
27100 Pavia, %
Italy\label{pavia}
\and
IBM Italia s.p.a. %
Circonvallazione Idroscalo , %
20090 Segrate (MI), %
Italy\label{ibm}
\and
Department of Physics, University of Z\"urich, %
CH-8057 Z\"urich, 
Switzerland\label{uzh}
\and
Universit\`a di Torino, Dipartimento di Fisica and INFN, Sezione di Torino, %
Via P. Giuria 1, %
10125 Torino, %
Italy\label{unito}
\and
Institute for Theoretical Physics, Karlsruhe Institute of
Technology (KIT), %
Karlsruhe, 
Germany\label{kit}
\and
DESY Theory Group, %
Notkestr. 85, %
D-22607 Hamburg, 
Germany\label{desy}
\and
Nikhef,
Science Park 105,
1098XG Amsterdam,
The Netherlancs\label{nikh}
}

@@

\subsection{Input parameters}

@@

\subsection{Three contributions}

@@

>>>>

%% Main-Version Draft
\documentclass[twocolumn,epjc3]{svjour3} % use the EPJC template, two columns
%%\documentclass[epjc3]{svjour3} % use the EPJC template, one column
\smartqed  % flush right qed marks, e.g. at end of proof
%% -------------------------------
%% |          Packages           |
%% -------------------------------
 \usepackage{amsmath}
 \usepackage{graphicx}
 \usepackage[merge,numbers,compress]{natbib}
 \usepackage[T1]{fontenc}
 \usepackage{booktabs}
 \usepackage{xcolor} 
 \usepackage{xspace}
 \usepackage{dcolumn}
 \usepackage{hyperref}
%  \usepackage[draft]{hyperref}
 \usepackage{caption}
 \usepackage{tabularx}
 \usepackage{lmodern}
 \usepackage{siunitx}
% \usepackage
% [subrefformat=parens,position=top,skip=-15pt,margin=15pt,justification=justified,singlelinecheck=false]
% {subcaption}

@@

\author{Benedikt Biedermann\thanksref{wurz}
\and
Simon Brass\thanksref{sieg}
\and
Ansgar Denner\thanksref{wurz}
\and
Stefan Dittmaier\thanksref{frei}
\and
Pietro Govoni\thanksref{mila}
\and
Michele Grossi\thanksref{pavia,ibm}
\and
Alexander Karlberg\thanksref{uzh} 
\and
Mathieu Pellen\thanksref{wurz}
\and
Giovanni  Pelliccioli\thanksref{unito}
\and
Simon Pl\"atzer\thanksref{wien}
\and
Michael Rauch\thanksref{kit}
\and
J\"urgen Reuter\thanksref{desy}
\and
Vincent Rothe\thanksref{desy} 
\and
Christopher Schwan\thanksref{frei}
\and
Pascal Stienemeier\thanksref{desy}
\and
Marco Zaro\thanksref{nikh}
}

% \thankstext{e1}{e-mail: mpellen@physik.uni-wuerzburg.de}
% \thankstext{e2}{e-mail: m.zaro@nikhef.nl}

\institute{Universit\"at W\"urzburg, %
Institut f\"ur Theoretische Physik und Astrophysik,  %
Emil-Hilb-Weg 22, %
97074 W\"urzburg, %
Germany\label{wurz} 
\and
Universit\"at Siegen, Department Physik, %
 Walter-Flex-Str.3, %
57068 Siegen, Germany\label{sieg}
\and
Albert-Ludwigs-Universit\"at Freiburg, Physikalisches Institut, %
 Hermann-Herder-Str.\ 3, %
79104 Freiburg, Germany\label{frei}
\and
Milan, Italy\label{mila}
\and
Universit\'a di Pavia, Dipartimento di Fisica and INFN, Sezione di Pavia, %
Via A. Bassi 6, %
27100 Pavia, %
Italy\label{pavia}
\and
IBM Italia s.p.a. %
Circonvallazione Idroscalo , %
20090 Segrate (MI), %
Italy\label{ibm}
\and
Department of Physics, University of Z\"urich, %
CH-8057 Z\"urich, 
Switzerland\label{uzh}
\and
Universit\`a di Torino, Dipartimento di Fisica and INFN, Sezione di Torino, %
Via P. Giuria 1, %
10125 Torino, %
Italy\label{unito}
\and
Particle Physics, Faculty of Physics, University of Vienna, %
Vienna, %
Austria\label{wien}
\and
Institute for Theoretical Physics, Karlsruhe Institute of
Technology (KIT), %
Karlsruhe, 
Germany\label{kit}
\and
DESY Theory Group, %
Notkestr. 85, %
D-22607 Hamburg, 
Germany\label{desy}
\and
Nikhef,
Science Park 105,
1098XG Amsterdam,
The Netherlands\label{nikh}
}

@@

\subsection{Input parameters}
\label{subsec:inputpar}

@@

\subsection{Three contributions}
\label{subsec:contributions}

@@

\subsection{Comparison in the fiducial region}
\label{subsec:LOfiducial}

### 2018-01-12 Draft/introduction.tex
Writting further paragraphs for the first part
Add a motivation and extend the introduction
- added a motivation (first paragraph)
- extended or added some explanations
- changed the process to include the `+ X`, since we are inclusive;
  TODO: make sure this is also used in the remaining document
- changes `section` and `Section` to `Sec.` if they are not at the
  beginning of a sentence (in `macros.tex` there are abbreviations for
  it so I assume that is the "correct" style)
- corrected some spelling mistakes

The vector-boson scattering (VBS) process with two positively charged W boson is now starting to be measured at the LHC~\cite{Aad:2014zda,Aaboud:2016ffv,Khachatryan:2014sta}.
A whole class of new processes will therefore be measured during Run~II at the Large Hadron Collider (LHC).
For now the measurements of VBS processes are limited by statistics but the situation will change in a near future.
On the theoretical side, it is thus of prime importance to provide precise predictions and infer their related systematic errors.

The $\PW^+\PW^+$ scattering is the simplest VBS processes to compute theoretically and to measure experimentally due to its particular charge structure and low background, respectively.
Therefore, it is an ideal example for a detailed study of various theoretical predictions.
In the last few years, several leading order (LO) and next-to-leading order (NLO) computations become available for both the VBS process~\cite{Jager:2009xx,Jager:2011ms,Denner:2012dz,Rauch:2016pai} and its QCD-induced irreducible background
process~\cite{Melia:2010bm,Melia:2011gk,Campanario:2013gea,Baglio:2014uba,Rauch:2016pai}.
These computations all relied on approximations while recently the complete NLO corrections became available \cite{Biedermann:2017bss}.
It is therefore interesting to infer in details the quality of the various approximations.
Indeed, apart from Ref.~\cite{Biedermann:2017bss} where it is commented on, \MP{more references?} no detailed comparison of the VBS approximations have been carried out.

The hadronic process is ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ and it posses three contributions at leading order.
The orders of the contributions are $\mathcal{O}{\left(\alpha^{6}\right)}$, $\mathcal{O}{\left(\alpha_{\rm s}\alpha^{5}\right)}$, and $\mathcal{O}{\left(\alphas^{2}\alpha^{4}\right)}$.
They are refer to as electroweak (EW), interference, and QCD contributions respectively.
\footnote{The EW contribution is sometimes referred to as the VBS contribution even it possesses non-VBS contributions.}
Therefore, the present work starts with a LO study of these three contributions as a function of typical VBS cuts.
This allows to identify the various contributions to the final state $\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$.
This is followed by a LO comparison between the various predictions at the level of the cross section and differential distributions.

At NLO, the process possesses four contributions of orders 
$\mathcal{O}{\left(\alpha^{7}\right)}$,
$\mathcal{O}{\left(\alphas\alpha^{6}\right)}$,
$\mathcal{O}{\left(\alphas^{2}\alpha^{5}\right)}$, and
$\mathcal{O}{\left(\alphas^{3}\alpha^{4}\right)}$.
The largest one is the EW corrections of order $\mathcal{O}{\left(\alpha^{7}\right)}$ \cite{Biedermann:2016yds,Biedermann:2017bss}.
The contribution of order $\mathcal{O}{\left(\alphas\alpha^{6}\right)}$ is the second largest NLO contribution.
It is often referred to as the QCD corrections to the VBS process.
In the following, this order is the one where our comparisons are focused on.
It is therefore usually referred to as simply \emph{NLO}.
As for the LO study, the various predictions are compared at the level of the cross section and differential distributions.
In particular, this allows to infer the accuracy of the so-called VBS approximation.
To our knowledge, such a detailed study was still missing.

@@

The article is organised as follow:
in the first part (section~\ref{sec:definition}), the process studied is defined.
Then, various approximation at LO and NLO are described in section~\ref{sec:details}.
It is followed by a presentation of the various programs used for the simulations.
Sections~\ref{sec:LO} and \ref{sec:NLO} are devoted to a LO and NLO study, respectively.
Section~\ref{sec:matching} deals with the matching to parton shower.
The last section (section \ref{sec:conclusion}) consists in concluding remarks and recommendations for experimental collaborations.

>>>>

Vector-boson scattering (VBS) is a class of processes that allow to probe the nature of Higgs-vector-vector couplings and quartic gauge couplings.
It is usually understood that VBS refers to the scattering of massive vector-bosons ($\PW^\pm,\PZ$), which therefore couple to the Higgs and can be longitudinally polarized.
The scattering of longitudinally polarized bosons is of particular interest, because the corresponding matrix elements feature both gauge- and unitarity cancellations that strongly depend on the actual form of the Higgs-sector.
A detailed study of this class of processes will therefore further constrain the Higgs-couplings and hint at or exclude non-standard model Higgs bosons.

The process with two positively charged W boson is the VBS process with the largest signal-background ratio at the LHC, for which evidence has been found in \SI{8}{\tera\electronvolt} data~\cite{Aad:2014zda,Khachatryan:2014sta} and which is now started to be observed~\cite{Sirunyan:2017ret} and measured~\cite{Aaboud:2016ffv} in \SI{13}{\tera\electronvolt} data.
For now the measurements of VBS processes are limited by statistics but the situation will change in a near future.
On the theoretical side, it is thus of prime importance to provide precise predictions and infer their related systematic errors.

The $\PW^+\PW^+$ scattering is the simplest VBS process to calculate, because the double-charge structure of the leptonic final state limits the number of partonic processes and total number of Feynman diagrams for each process.
It also implies that irreducible backgrounds are comparatively small, which make this VBS process experimentally favourable in comparison to \eg $\PW^+\PW^-$ scattering, which has the largest cross section.
Therefore, it is an ideal candidate for a detailed study of various theoretical predictions.

In the last few years, several leading order (LO) and next-to-leading order (NLO) computations became available for both the VBS process~\cite{Jager:2009xx,Jager:2011ms,Denner:2012dz,Rauch:2016pai} and its QCD-induced irreducible background process~\cite{Rauch:2016pai,Melia:2010bm,Melia:2011gk,Campanario:2013gea,Baglio:2014uba}.
These computations all rely on approximations, while recently the complete NLO corrections have been performed~\cite{Biedermann:2017bss}.
It is therefore interesting to infer in details the quality of the various approximations.
Indeed, apart from Ref.~\cite{Biedermann:2017bss} where it is commented on, \MP{more references?} no detailed comparison of the VBS approximations have been carried out.
Preliminary results have already been made public in Ref.~[proceedings Split].

The hadronic process is $\Pp\Pp\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}\,\Pj\Pj+\mathrm{X}$, which includes the $\PW^+\PW^+$ scattering.
This final state possesses three contributions at LO whose coupling orders are $\mathcal{O}{\left(\alpha^{6}\right)}$, $\mathcal{O}{\left(\alpha_{\rm s}\alpha^{5}\right)}$, and $\mathcal{O}{\left(\alphas^{2}\alpha^{4}\right)}$.
They are commonly referred to as electroweak (EW), interference, and QCD contributions, respectively.%
\footnote{The EW contribution is sometimes referred to as the VBS contribution even it possesses non-VBS contributions.}
Therefore, the present work starts with a LO study of these three contributions as a function of typical VBS cuts.
This allows to identify the various contributions to the final state $\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}\,\Pj\Pj$.
This is followed by a LO comparison between the various predictions at the level of the cross section and differential distributions.

At NLO, the process possesses four contributions of orders $\mathcal{O}{\left(\alpha^{7}\right)}$, $\mathcal{O}{\left(\alphas\alpha^{6}\right)}$, $\mathcal{O}{\left(\alphas^{2}\alpha^{5}\right)}$, and $\mathcal{O}{\left(\alphas^{3}\alpha^{4}\right)}$.
The largest one are the EW corrections~\cite{Biedermann:2017bss,Biedermann:2016yds} of order $\mathcal{O}{\left(\alpha^{7}\right)}$.
The contribution to the order $\mathcal{O}{\left(\alphas\alpha^{6}\right)}$ is the second largest NLO contribution and is often referred to as the QCD corrections to the VBS process.
In the following, this order is the one where our comparisons are focused on; in this article we will refer to it as simply \emph{NLO}.
As for the LO study, the various predictions are compared at the level of the cross section and differential distributions.
In particular, this allows to infer the accuracy of the so-called VBS approximation, which we will define in later.
To our knowledge, such a detailed study was still missing.

@@

The article is organised as follow:
In Sec.~\ref{sec:definition} the studied process is defined.
Various approximation at LO and NLO are described in Sec.~\ref{sec:details}.
This is followed by a presentation of the programs used for the computations.
Sections~\ref{sec:LO} and \ref{sec:NLO} are devoted to a LO and NLO study, respectively.
Section~\ref{sec:matching} deals with the matching to parton shower.
The last section consists in concluding remarks and recommendations for experimental collaborations.
